Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-11-30 paper/paper.tex
Don't use multicols, it upsets AAAI
Murican

\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{complexity}
\usepackage{microtype}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{cleveref}
\usepackage{tikz}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage[vlined]{algorithm2e}

@@

\begin{multicols}{2}

@@

@@

\end{multicols}
\vspace{0.5cm}% Be careful if you remove this! Something weird happens where the caption overlaps
% the algorithm due to algorithm2e and multicol[vlined] not being entirely happy with each other.
% If you take this out, please check the space between the algorithm and the caption very very
% carefully.

@@

\begin{figure}[h!]% The ! is needed to avoid this being bumped forward a page
    \centering
    \includegraphics*{gen-graph-which-k-by-family.pdf}
    \caption{The proportion of instances, in different families, which become satisfiable for
    increasing values of $k$. The ``larger'' instances are those where we can prove unsatisfiability for
    $k = 5$, whilst the gap between the top of the bar and the top of the graph is the fraction of
    instances where a timeout was reached for at least one value of $k$.}\label{figure:which-k}
\end{figure}

@@

\subsection{Solving from the Top Down}\label{section:topdown}

>>>>

\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{complexity}
\usepackage{microtype}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{cleveref}
\usepackage{tikz}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage[vlined]{algorithm2e}

@@

    \begin{minipage}[t]{\dimexpr.5\textwidth-.5\columnsep}

@@

\end{minipage}\hfill%
    \begin{minipage}[t]{\dimexpr.5\textwidth-.5\columnsep}

@@

\end{minipage}

@@

\begin{figure}[ht!] % This is necessary to avoid really awful figure placement midway through the
    % references...
    \centering
    \includegraphics*{gen-graph-which-k-by-family.pdf}
    \caption{The proportion of instances, in different families, which become satisfiable for
    increasing values of $k$. The ``larger'' instances are those where we can prove unsatisfiability for
    $k = 5$, whilst the gap between the top of the bar and the top of the graph is the fraction of
    instances where a timeout was reached for at least one value of $k$.}\label{figure:which-k}
\end{figure}

@@

\subsection{Solving From the Top Down}\label{section:topdown}
